### 2017-06-15 manuscript/manuscript.Rmd
Make proper tables.

keywords          : "reproducibility; version control; git; research methods; open science"
wordcount         : "X"
bibliography      : ["references.bib"]
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
lang              : "english"
class             : "doc, 12pt, draftfirst"  # man / jou / doc
output            : papaja::apa6_pdf
---

@@

<!-- Examples of problems in psychology solved by VCS. -->
\noindent
\fbox{\begin{minipage}{\textwidth}
  \begin{itemize}
    \item Problem: Researchers want to try different ways of visualizing and modeling their data, and keep track of all the different versions they try.
      \begin{itemize}
        \item Solution: VCS allows researchers to save each version of the analysis into a history from where it can be easily recalled. This approach also eschews the need for creating multiple copies of the same analysis files with small tweaks, as illustrated \href{http://phdcomics.com/comics/archive.php?comicid=1531}{here}.
      \end{itemize}
  \end{itemize}
  \begin{itemize}
    \item Problem:
      \begin{itemize}
        \item Solution:
      \end{itemize}
  \end{itemize}
\end{minipage}}

@@

## Further resources for learning Git

\noindent
\fbox{\begin{minipage}{\textwidth}
  \begin{itemize}
    \item \href{https://www.git-tower.com/blog/workflow-of-version-control}{Basic VCS workflow}, an infographic explaining how VCS works.
    \item \href{https://services.github.com/resources/cheatsheets/}{GitHub's Git cheat sheet} is available in multiple languages and contains the most used Git commands.
    \item \href{https://try.github.io/levels/1/challenges/1}{TryGit}, an interactive website for learning the basics of Git.
    \item \href{http://r-pkgs.had.co.nz/git.html}{Git + GitHub} in an R programming context.
    \item \href{https://git-scm.com/book/en/v2}{Pro Git book}, a complete manual of Git.
  \end{itemize}
\end{minipage}}

\newpage

>>>>

keywords          : "reproducibility; version control; git; research methods; open science"
wordcount         : "X"
bibliography      : ["references.bib"]
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
lang              : "english"
class             : "doc, 12pt, draftfirst"  # man / jou / doc
output            : papaja::apa6_pdf
header-includes:
   - \usepackage{tcolorbox}
---

@@

<!-- Examples of problems in psychology solved by VCS. -->
\begin{tcolorbox}[colframe=green!50!black, colback=green!5, fonttitle=\small\bfseries, fontupper=\footnotesize, title=Box 1. Common problems and their VCS solutions]
    \begin{itemize}
    \item How to try different ways of visualizing and modeling data while keeping track of the different versions---and the differences between them?
        \begin{itemize}
        \item VCS saves each version of the analysis, allowing testing new features without losing previous versions or proliferating files in the project's directories. All the past versions can be directly compared with each other.
        \end{itemize}
    \end{itemize}
    \begin{itemize}
    \item How to work on the same code or manuscript files simultaneously with collaborators?
        \begin{itemize}
        \item VCS were built for distributed collaborative work: Collaborators work on their local copies and "push" and "pull" material to and from each other or a central "repository". VCS keeps precise track of who has done what, when, and (possibly) why.
        \end{itemize}
    \end{itemize}
    \begin{itemize}
    \item How to share my work in an organized manner with others?
        \begin{itemize}
        \item VCS requires committing to a common organization scheme with collaborators, making it easier to keep everyone "on the same page" with what goes where and how to contribute to specific parts of the project. Sharing the project with others is built into VCS, and can be facilitated with online services such as GitHub.
        \end{itemize}
    \end{itemize}
\end{tcolorbox}

@@

<!-- Box 2. Further resources for learning Git -->
\begin{tcolorbox}[colframe=green!50!black, colback=green!5, fonttitle=\small\bfseries, fontupper=\footnotesize, title=Box 2. Further resources for learning Git]
\begin{itemize}
    \item \href{https://www.git-tower.com/blog/workflow-of-version-control}{Basic VCS workflow}, an infographic explaining how VCS works (\url{https://www.git-tower.com/blog/workflow-of-version-control}).
    \item \href{https://services.github.com/resources/cheatsheets/}{GitHub's Git cheat sheet} is available in multiple languages and contains the most used Git commands (\url{https://services.github.com/resources/cheatsheets/}).
    \item \href{https://try.github.io}{TryGit}, an interactive website for learning the basics of Git (\url{https://try.github.io}).
    \item \href{http://r-pkgs.had.co.nz/git.html}{Git + GitHub} in an R programming context (\url{http://r-pkgs.had.co.nz/git.html}).
    \item \href{https://git-scm.com/book/en/v2}{Pro Git book}, a complete manual of Git (\url{https://git-scm.com/book/en/v2}).
\end{itemize}
\end{tcolorbox}
\newpage
